\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}

\onehalfspacing

\title{Transforming How We Diagnose Heart Disease}
\author{Kyle Daruwalla and Alvin (Yuxanxiang) Ye}
\date{\today}

\begin{document}
	
\maketitle

\section{Project Details}

\subsection{Overview}
In the medical community, the popular method for diagnosing heart disease is analyzing patient magnetic resonance images (MRIs). However, this can be a time consuming process for doctors that takes away from valuable patient time. Our goal is to make this process simpler and more efficient by using machine learning and image recognition.

\subsection{Objectives}
In order to concisely describe the project goals, we have created the following project objectives:
\begin{enumerate}
	\item Analyze MRIs using image recognition to identify regions of interest (ROIs). Regions of interest are defined as a single chamber of the heart.
	\item Calculate the total volume of a chamber of the heart at the beginning and middle of a heart beat.
	\item Derive the ejection fraction (EF) using the total volumes. The EF represents the percentage blood ejected from the left ventricle with each heartbeat.
	\item Use machine learning (decision trees and neural networks) to predict heart disease risk based on the total volumes and EF of the training data.
\end{enumerate}

\section{Team}
\textbf{Team Leader:} Kyle Daruwalla
\textbf{Team Member(s):} Alvin Ye

\section{Project Breakdown}

\subsection{Tasks}
\begin{center}
	\begin{tabular}{|c|c|c|c|}
		\hline
		Task ID & Description & Assigned To & Difficulty \\
		\hline
		T0 & Play with training data to find how doctors diagnose patients & Kyle & Minor \\
		T1 & Understanding image recognition example algorithm & Alvin & Normal \\
		T2 & Understanding deep learning example algorithm & Kyle & Normal \\
		T3 & Apply image processing to full data set & Alvin & Severe \\
		T4 & Design a decision tree for data generated & Kyle & Normal \\
		T5 & Apply deep learning algorithms to subset of data & Kyle & Severe \\
		T6 & Refine the decision tree for better results & Alvin & Normal \\
		T7 & Train deep learning algorithm on training data & Kyle & Normal \\
		T8 & Refine deep learning algorithm & Alvin & Severe \\
		\hline
	\end{tabular}
\end{center}

\subsection{Timeline}
Below is the milestone timeline and task organization.
\begin{center}
	\begin{tabular}{|c|c|c|}
		\hline
		Milestone ID & Description & Due Date \\
		\hline
		M0 & Data Acquisition Report & 15 Jan 2016 \\
		M1 & Preliminary Results Report & 29 Jan 2016 \\
		M2 & Project Draft Report & 19 Feb 2016 \\
		M3 & Final Report & 26 Feb 2016 \\
		M4 & First Kaggle Submission & 29 Feb 2016 \\
		M5 & Final Kaggle Submission & 14 Mar 2016 \\
		\hline
	\end{tabular}
\end{center}
\begin{center}
	\begin{tabular}{|c|c|c|c|}
		\hline
		Task ID & Milestone ID & Repeating? & First Due Date \\
		\hline
		T0 & M0 & No & 13 Jan 2016 \\
		T1 & M0 & No & 15 Jan 2016 \\
		T2 & M0 & No & 15 Jan 2016 \\
		T3 & M1 & No & 20 Jan 2016 \\
		T4 & M1 & No & 20 Jan 2016 \\
		T5 & M2 & Weekly & 30 Jan 2016 \\
		T6 & M2/M3/M4/M5 & Weekly & 30 Jan 2016 \\
		T7 & M3/M4/M5 & No & 19 Feb 2016 \\
		T8 & M4/M5 & Weekly & 24 Feb 2016 \\
		\hline
	\end{tabular}
\end{center}

\end{document}